metric-learn: Metric Learning Algorithms in Python

### 2020-06-22 metric-learn-jmlr.tex
knitpick
Address final comments

\texttt{metric-learn} is an open source package for metric learning in Python, which implements many popular metric-learning algorithms with different levels of supervision through a unified interface.
%\footnote{This makes \texttt{metric-learn} stand out from other packages, like \texttt{PyDML} (\url{https://github.com/jlsuarezdiaz/pyDML}) which focuses on supervised metric learning algorithms.}
% (not only class supervision, unlike most packages are focused on, including another package for metric learning in Python, \texttt{PyDML})
% , which is one interesting feature allowed by the metric learning paradigm. 
Its API is compatible with \texttt{scikit-learn} \citep{scikit-learn}, a prominent machine learning library in Python. This allows for streamlined model selection, evaluation, and pipelining with other estimators.
Other packages for metric learning already exist, however, they have a different focus: \texttt{DistLearn}\footnote{\url{https://www.cs.cmu.edu/~liuy/distlearn.htm}} and \texttt{pyDML}\footnote{\url{http://github.com/jlsuarezdiaz/pydml}} contain almost only fully supervised or unsupervised metric learning algorithms, and \texttt{pytorch-metric-learning}\footnote{\url{http://github.com/KevinMusgrave/pytorch-metric-learning}} is focused on deep metric learning, using the pytorch framework.
% The project is developed collaboratively through GitHub, its code is thoroughly tested using continuous integration tools. It was recently included to \texttt{scikit-learn-contrib}, which hosts high-quality \texttt{scikit-learn}-compatible projects.\footnote{\url{https://github.com/scikit-learn-contrib/scikit-learn-contrib}}
%\aurelien{decide if we include or not a few sentences on positioning wrt other packages}

%, which makes \texttt{metric-learn} stand out from other packages, like \texttt{PyDML} \footnote{\url{https://github.com/jlsuarezdiaz/pyDML}}, which mostly focuses on supervised metric learning algorithms.
% Acknowledgements should go at the end, before appendices and references
%The rest of this paper is organized as follows. We first present an overview of the package, followed by a more detailed description of the available algorithms. We then give more details about the API and the software architecture, in particular the compatibility with \texttt{scikit-learn}, and conclude with a discussion of future developments.

@@

% use t to put figure on top (preferred) Thanks ! 
\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.12\textwidth} % "0.45" donne ici la largeur de l'image
        \centering \includegraphics[scale=0.35]{labels.pdf}
        \caption{class}\label{fig:full}
    \end{subfigure}
    \begin{subfigure}[t]{0.20\textwidth}
        \centering \includegraphics[scale=0.35]{pairs.pdf}
        \caption{pair}\label{fig:pairs}
    \end{subfigure}
    \begin{subfigure}[t]{0.31\textwidth}
        \centering \includegraphics[scale=0.35]{triplets.pdf}
	\caption{triplet}\label{fig:triplets}
    \end{subfigure}
    \begin{subfigure}[t]{0.31\textwidth}
        \centering \includegraphics[scale=0.35]{quadruplets.pdf}
        \caption{quadruplet}\label{fig:quadruplets}
    \end{subfigure}
    \caption{Different types of supervision for metric learning %(\subref{fig:full}) Class supervision: make samples from the same label (here, identity) closer together than samples from different labels. (\subref{fig:pairs}) Pair supervision: make similar pairs (here, corresponding to the same person) to be closer than dissimilar pairs (different persons). (\subref{fig:quadruplets}) Quadruplet supervision: make leftmost pairs (here, people of similar age) closer than rightmost pairs (of bigger age difference).
    illustrated on face image data taken from the Labeled Faces in the Wild dataset \citep{Huang12}.}\label{fig:flowers}
\end{figure}

>>>>

\texttt{metric-learn} is an open source package for metric learning in Python, which implements many popular metric-learning algorithms with different levels of supervision through a unified interface.
%\footnote{This makes \texttt{metric-learn} stand out from other packages, like \texttt{PyDML} (\url{https://github.com/jlsuarezdiaz/pyDML}) which focuses on supervised metric learning algorithms.}
% (not only class supervision, unlike most packages are focused on, including another package for metric learning in Python, \texttt{PyDML})
% , which is one interesting feature allowed by the metric learning paradigm. 
Its API is compatible with \texttt{scikit-learn} \citep{scikit-learn}, a prominent machine learning library in Python. This allows for streamlined model selection, evaluation, and pipelining with other estimators.
Other packages for metric learning already exist, however, they have a different focus: \texttt{pyDML} \footnote{\url{http://github.com/jlsuarezdiaz/pydml}} contains almost only fully supervised or unsupervised metric learning algorithms, and \texttt{pytorch-metric-learning} \footnote{\url{http://github.com/KevinMusgrave/pytorch-metric-learning}} is focused on deep metric learning, using the \texttt{pytorch} \citep{pytorch} framework. There is also a Matlab toolkit, \texttt{DistLearn} \footnote{\url{https://www.cs.cmu.edu/~liuy/distlearn.htm}}, that is a webpage gathering several implementations of metric-learning algorithms, however they are mostly fully supervised or unsupervised, and they lack a common interface.
% The project is developed collaboratively through GitHub, its code is thoroughly tested using continuous integration tools. It was recently included to \texttt{scikit-learn-contrib}, which hosts high-quality \texttt{scikit-learn}-compatible projects.\footnote{\url{https://github.com/scikit-learn-contrib/scikit-learn-contrib}}
%\aurelien{decide if we include or not a few sentences on positioning wrt other packages}
%, which makes \texttt{metric-learn} stand out from other packages, like \texttt{PyDML} \footnote{\url{https://github.com/jlsuarezdiaz/pyDML}}, which mostly focuses on supervised metric learning algorithms.
% Acknowledgements should go at the end, before appendices and references
%The rest of this paper is organized as follows. We first present an overview of the package, followed by a more detailed description of the available algorithms. We then give more details about the API and the software architecture, in particular the compatibility with \texttt{scikit-learn}, and conclude with a discussion of future developments.

@@

% use t to put figure on top (preferred) Thanks ! 
\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{0.12\textwidth} % "0.45" donne ici la largeur de l'image
        \centering \includegraphics[scale=0.35]{labels.pdf}
        \caption{classes}\label{fig:full}
    \end{subfigure}
    \begin{subfigure}[t]{0.20\textwidth}
        \centering \includegraphics[scale=0.35]{pairs.pdf}
        \caption{pairs}\label{fig:pairs}
    \end{subfigure}
    \begin{subfigure}[t]{0.31\textwidth}
        \centering \includegraphics[scale=0.35]{triplets.pdf}
	\caption{triplets}\label{fig:triplets}
    \end{subfigure}
    \begin{subfigure}[t]{0.31\textwidth}
        \centering \includegraphics[scale=0.35]{quadruplets.pdf}
        \caption{quadruplets}\label{fig:quadruplets}
    \end{subfigure}
    \caption{Different types of supervision for metric learning %(\subref{fig:full}) Class supervision: make samples from the same label (here, identity) closer together than samples from different labels. (\subref{fig:pairs}) Pair supervision: make similar pairs (here, corresponding to the same person) to be closer than dissimilar pairs (different persons). (\subref{fig:quadruplets}) Quadruplet supervision: make leftmost pairs (here, people of similar age) closer than rightmost pairs (of bigger age difference).
    illustrated on face image data taken from the Labeled Faces in the Wild dataset \citep{Huang12}.}\label{fig:flowers}
\end{figure}
